---
title: "Part 7 Assignment"
author: "You"
date: "2/17/2021"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
clinical <- readr::read_csv(here("data/part1/clinical.csv"),  na="NA") %>%
  filter(!is.na(tumor_stage))

clinical_list <- clinical %>%
  group_by(tumor_stage) %>%
  group_split(.keep=TRUE)
  
clinical_names <- clinical %>%
  group_by(tumor_stage) %>%
  group_keys() %>% unlist() 

names(clinical_list) <- clinical_names
```



1. Write a function called `make_table()` that takes as an input a `df` (`data.frame`) and runs `janitor::tabyl` on the `vital_status` and `race` columns.

Use it on one of the slots in `clinical_list`.

```{r}
make_table <- function(df){
  out_table <- df %>% 
    janitor::tabyl(------, ------)
  return(out_table)  
}

make_table(---------)
```

2. Use `map()` to apply `make_table` to `clinical_list`.

```{r}
tumor_tables <- map(-------, -------)
tumor_tables
```

3. For the data files in `data/part2`, use the `load_csv_files()` function to load the datasets.

```{r functions}
load_csv_files <- function(path = "data/part2/LUSC.csv"){
  out_frame <- read_csv(path, na="NA")
  out_frame <- janitor::clean_names(out_frame) %>%
    mutate(source=path)
  return(out_frame)
}
```

```{r}
part2_files <- list.files(here("data/part2"), full.names = TRUE, pattern="csv")
part2_files

part2_dfs <- map(part2_files, ------------)
names(part2_dfs) <- part2_files
```

Confirm you have loaded the data correctly. You can do this by showing a slot or by showing the whole list.

```{r}


```

4. Write a function called `plot_boxplot()` to make a boxplot with x = `tumor_stage` and y = `cigarettes_per_day`, and fill = `tumor_stage` from an input `data.frame` called `df`. 

Use the function on the first slot of 


```{r}
plot_boxplot <- function(df){
  plot_title <- df$source[1]
  
  out_plot <- ggplot(df) +
    aes(--------------------) +
    ----------------- +
    labs(title = plot_title)

  return(out_plot)
}

plot_boxplot(part2_dfs[[1]])
```


5. Use `map()` to apply this function to `part2_dfs`. You don't have to assign it to a list.

```{r}
map(---------, ----------)

```